### 2023-08-14 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny

%%%TITLE, AUTHORS AND ABSTRACT%%%
\twocolumn[
  \begin{@twocolumnfalse}
{\includegraphics[height=30pt]{head_foot/SM}\hfill\raisebox{0pt}[0pt][0pt]{\includegraphics[height=55pt]{head_foot/RSC_LOGO_CMYK}}\\[1ex]
\includegraphics[width=18.5cm]{head_foot/header_bar}}\par
\vspace{1em}
\sffamily
\begin{tabular}{m{4.5cm} p{13.5cm} }
%
\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{Hydrodynamics of Multicomponent Vesicles Under Strong Confinement}} \\
\vspace{0.3cm} & \vspace{0.3cm} \\
%
 & \noindent\large{Ashley Gannon,\textit{$^{a}$} Y.-N. Young,\textit{$^{b\ddag}$} and Bryan Quaife\textit{${\ast}${$^{a}$}}} \\
% %Author names go here instead of "Full name", etc.
%
\includegraphics{head_foot/dates} & \noindent\normalsize{The abstract should be a single paragraph which summarises the content of the article. Any references in the abstract should be written out in full \textit{e.g.}\ [Surname \textit{et al., Journal Title}, 2000, \textbf{35}, 3523].} \\%The abstrast goes here instead of the text "The abstract should be..."
%
\end{tabular}
%
 \end{@twocolumnfalse} \vspace{0.6cm}
]
%%%END OF TITLE, AUTHORS AND ABSTRACT%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:LL} Lubrication layers and excess pressure}
The lubrication layer between a vesicle and the solid wall plays a
critical role on the vesicle's dynamics. Therefore, throughout
Section~\ref{sec:results}, we calculate the size and analyze the flow
inside the lubrication layers. 
%We first justify the use of the term `lubrication layer' by verifying
%that the flow velocity is parabolic between the vesicle and the solid
%wall. Figure~\ref{fig:quadraticProof} illustrates the horizontal
%velocity (solid line) and the corresponding best fit quadratic (dashed
%line) in the co-moving frame, and the profiles agree.
%
%\begin{figure}[H]
%    \centering
%    \includegraphics[width=\columnwidth]{figures/lubricationLayer_quadratic.pdf}  
%    \caption{The co-moving velocity profile in the top and bottom lubrication layers. The red curve is the velocity profile, the dashed black line is the best quadratic fit.}
%    \label{fig:quadraticProof}
%\end{figure}
To define the size of the top lubrication layer (the size of the bottom
lubrication layer is defined similarly), we let
$d(\xx,\Gamma_\mathrm{top})$ be the minimum distance between a point on
the vesicle, $\xx \in \gamma$, and the top half of the confining
geometry.
%\begin{align}
%    d(\xx,\Gamma_\mathrm{top}) = \inf_{\yy \in \Gamma_\mathrm{top}} \|\xx-\yy\|,
%\end{align}
%where $\Gamma_{\mathrm{top}}$ is the top portion of $\Gamma$.
We find all local minimums of $d(\xx,\Gamma_\mathrm{top})$, with
the condition that $d(\xx,\Gamma_\mathrm{top}) < \delta$, where $\delta$
is a parameter. If no such local minimums exist, then the vesicle is too
far from $\Gamma_\mathrm{top}$ to define a lubrication layer. If there
are two or more local minimums, the left-most, $\xx_L$, and right-most,
$\xx_R$, local minimums form the start and end of the lubrication layer.
If there is only one local minimum, then $\xx_L$ and $\xx_R$ are the
points on $\gamma$ to the left and right of this local minimum with the
condition that $d(\xx_L,\Gamma_\mathrm{top}) =
d(\xx_R,\Gamma_\mathrm{top}) = \delta$. Then, the segment
$\gamma_{\mathrm{layer}} \subset \gamma$ consists of all points $\xx \in
\gamma$ between $\xx_L$ and $\xx_R$ with the condition that
$d(\xx,\Gamma_\mathrm{top}) < \delta$. Finally, the lubrication layer
width is
\begin{align}
  w_\mathrm{top} = \frac{1}{|\gamma_{_\mathrm{layer}}|} 
    \int_{\gamma_{_\mathrm{layer}}} d(\xx,\Gamma_\mathrm{top}) \, ds.
\end{align}
The region that defines the top and bottom lubrication layers is
illustrated in Figure~\ref{fig:schematic}, and the height of the gray
regions denote the lubrication layer thickness. In this example, the top
layer is broken across three different regions.

@@

A difference between the size of the top and bottom lubrication layers
indicates that the vesicle  has deviated from the center of the channel,
and this results in tank-treading behavior~\cite{aga-bir2020}.  To
determine if a vesicle is tank-treading, we calculate the tangential
velocity at several points on $\gamma$, and if this value is constant,
this is the tank-treading velocity.

@@

The size of the top and bottom lubrication layers are also related to
the excess pressure. The magenta curve on the top half of
Figure~\ref{fig:lubricationComposite} shows the excess pressure (with the
axis aligned on the right side of the plot). When the lubrication layers
are large, most notably for the multicomponent vesicle, less pressure is
required to force the vesicle through the geometry, and the result is a
smaller (less negative) excess pressure. In contrast, when the
lubrication layers are small, most notably for the stiff
single-component vesicle, more pressure is required to force the vesicle
through the geometry, and we the result is a larger (more negative)
excess pressure.

@@

As a multicomponent vesicle enters and exits a closely-fitted stenosis,
coarsening of the lipid domains is expedited. However, inside the
stenosis, the strong confinement hinders the coarsening as the vesicle
shape and the lipid distribution remain more or less unaltered as the
vesicle moves through the stenosis. Once inside a stenosis, we define
the lubrication layer and its width. We find that tank-treading along
the vesicle inside the stenosis is closely related to the asymmetry in
the lubrication layer width between the top and bottom walls. For
vesicles with a high reduced area the lubrication layer width is
symmetric between the top and bottom walls, and we find no tank-treading
along the membrane. On the other hand, for a vesicle with a lower
reduced area, the lubrication layer width is asymmetric and the vesicle
membrane tanks treads. Furthermore we also find that the excess pressure
(the additional pressure required to pass the vesicle through the
stenosis) is correlated to the size of the lubrication layer: a larger
lubrication layer size results in smaller excess pressure
%the larger the lubrication layer size, the smaller the excess pressure
%is.

>>>>

%%%TITLE, AUTHORS AND ABSTRACT%%%
\twocolumn[
  \begin{@twocolumnfalse}
{\includegraphics[height=30pt]{head_foot/SM}\hfill\raisebox{0pt}[0pt][0pt]{\includegraphics[height=55pt]{head_foot/RSC_LOGO_CMYK}}\\[1ex]
\includegraphics[width=18.5cm]{head_foot/header_bar}}\par
\vspace{1em}
\sffamily
\begin{tabular}{m{4.5cm} p{13.5cm} }
%
\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{Hydrodynamics of Multicomponent Vesicles Under Strong Confinement}} \\
\vspace{0.3cm} & \vspace{0.3cm} \\
%
 & \noindent\large{Ashley Gannon,\textit{$^{a}$} Y.-N. Young,\textit{$^{b\ddag}$} and Bryan Quaife\textit{${\ast}${$^{a}$}}} \\
% %Author names go here instead of "Full name", etc.
%
\includegraphics{head_foot/dates} & \noindent\normalsize{We numerically study the hydrodynamics of multicomponent vesicles in strong confinement as a simplified model for red blood cells going through extreme constriction.  Under strong confinement, we parametrize the bending modulus so that it is positive for all values of the lipid phase parameter. For a multicomponent vesicle going through a stenosis, we find the correlation between the lipid phase coarsening and the lubrication layer (such as size and flow profile), excess pressure, and tank treading in the membrane. For a multicomponent vesicle going through a contracting channel, we find that the lipid always phase separates so that the vesicle is stiffer in the front as it passes through the constriction.  For both cases of confinement we find that the lipid coarsening is arrested under strong confinement, and proceeds with high rate upon relief from extreme confinement. These results may be useful for efficient sorting lipid domains using microfluidic flows by controlled release of vesicles going through strong confinement. } \\%The abstrast goes here instead of the text "The abstract should be..."
%
\end{tabular}
%
 \end{@twocolumnfalse} \vspace{0.6cm}
]
%%%END OF TITLE, AUTHORS AND ABSTRACT%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:LL} Lubrication layers and excess pressure}
The lubrication layer between a vesicle and the solid wall plays a
critical role in the dynamics of a vesicle under strong confinement.
Therefore, throughout
Section~\ref{sec:results}, we calculate and analyze the flow
inside the lubrication layers between the vesicle and the channel walls to elucidate the correlation between hydrodynamics and membrane dynamics.
%We first justify the use of the term `lubrication layer' by verifying
%that the flow velocity is parabolic between the vesicle and the solid
%wall. Figure~\ref{fig:quadraticProof} illustrates the horizontal
%velocity (solid line) and the corresponding best fit quadratic (dashed
%line) in the co-moving frame, and the profiles agree.
%
%\begin{figure}[H]
%    \centering
%    \includegraphics[width=\columnwidth]{figures/lubricationLayer_quadratic.pdf}  
%    \caption{The co-moving velocity profile in the top and bottom lubrication layers. The red curve is the velocity profile, the dashed black line is the best quadratic fit.}
%    \label{fig:quadraticProof}
%\end{figure}
To define the size of the top lubrication layer (the size of the bottom
lubrication layer is defined similarly), we let
$d(\xx,\Gamma_\mathrm{top})$ be the minimum distance between a point on
the vesicle, $\xx \in \gamma$, and the top half of the confining
geometry.
%\begin{align}
%    d(\xx,\Gamma_\mathrm{top}) = \inf_{\yy \in \Gamma_\mathrm{top}} \|\xx-\yy\|,
%\end{align}
%where $\Gamma_{\mathrm{top}}$ is the top portion of $\Gamma$.
We find all local minimums of $d(\xx,\Gamma_\mathrm{top})$, with
the condition that $d(\xx,\Gamma_\mathrm{top}) < \delta$, where $\delta$
is a parameter. If no such local minimums exist, then the vesicle is too
far from $\Gamma_\mathrm{top}$ to define a lubrication layer. If there
are two or more local minimums, the left-most, $\xx_L$, and right-most,
$\xx_R$, local minimums form the start and end of the lubrication layer.
If there is only one local minimum, then $\xx_L$ and $\xx_R$ are the
points on $\gamma$ to the left and right of this local minimum with the
condition that $d(\xx_L,\Gamma_\mathrm{top}) =
d(\xx_R,\Gamma_\mathrm{top}) = \delta$. Then, the segment
$\gamma_{\mathrm{layer}} \subset \gamma$ consists of all points $\xx \in
\gamma$ between $\xx_L$ and $\xx_R$ with the condition that
$d(\xx,\Gamma_\mathrm{top}) < \delta$. Finally, the lubrication layer
width is
\begin{align}
  w_\mathrm{top} = \frac{1}{|\gamma_{_\mathrm{layer}}|} 
    \int_{\gamma_{_\mathrm{layer}}} d(\xx,\Gamma_\mathrm{top}) \, ds.
\end{align}
The region that defines the top and bottom lubrication layers is
illustrated in Figure~\ref{fig:schematic}, and the height of the gray
regions denote the lubrication layer thickness. In this example, the top
layer is broken across three different regions.

@@

A difference between the size of the top and bottom lubrication layers
indicates that the vesicle membrane shape is asymmetric with respect to 
the center of the channel,
and this results in tank-treading behavior~\cite{aga-bir2020}.  To
determine if a vesicle is tank-treading, we calculate the tangential
velocity at several points on $\gamma$, and if this value is constant,
this is the tank-treading velocity.

@@

The sizes of the top and bottom lubrication layers are also related to
the excess pressure. The magenta curve on the top half of
Figure~\ref{fig:lubricationComposite} shows the excess pressure (with the
axis aligned on the right side of the plot). When the lubrication layers
are large, most notably for the multicomponent vesicle, less pressure is
required to force the vesicle through the geometry, and the result is a
smaller (less negative) excess pressure. In contrast, when the
lubrication layers are small, most notably for the stiff
single-component vesicle, more pressure is required to force the vesicle
through the geometry, and we the result is a larger (more negative)
excess pressure.

@@

As a multicomponent vesicle enters and exits a closely-fitted stenosis,
coarsening of the lipid domains is expedited. However, inside the
stenosis, the strong confinement hinders the coarsening as the vesicle
shape and the lipid distribution remain nearly unaltered as the
vesicle moves through the stenosis. Once inside a stenosis, we define
the lubrication layer and its width. We find that tank-treading along
the vesicle inside the stenosis is closely related to the asymmetry in
the lubrication layer width between the top and bottom walls. For
vesicles with a high reduced area the lubrication layer width is
symmetric between the top and bottom walls, and we find no tank-treading
along the membrane. On the other hand, for a vesicle with a lower
reduced area, the lubrication layer width is asymmetric and the vesicle
membrane tanks treads. Furthermore we also find that the excess pressure
(the additional pressure required to pass the vesicle through the
stenosis) is correlated to the size of the lubrication layer: a larger
lubrication layer size results in smaller excess pressure.
%the larger the lubrication layer size, the smaller the excess pressure
%is.
